%% Show Preview - A Show emulator so you can preview your show with audio
%% Tim Clemans
%% CS 383
%% 3/8/2017
%%

\documentclass{article}

\begin{document}
	\section{Show Preview}
        The Show Preview will allow the user to run the animation they've created in an emulator, which will give them an accurate representation of what their show will look like when played on the grid size they've selected.
	\subsection{Mock-up}
	   % ADD Screenshot later
	   \{insert screenshot after final version\}
	\subsection{Functionality}
	\begin{itemize}
		\item Open Preview window or section 
		\begin{itemize}
		    \item A button or menu option that will bring up the Show Preview window.
		\end{itemize}
		\item Adjust playback grid size
		\begin{itemize}
		    \item The playback grid will default to whatever size the user initially set their show to. But there will be a way (inputs for number of rows and number of columns) for the user to change the grid size so they can see what their show might look like on smaller or larger grids.
		\end{itemize}
		\item Sync with Audio (optional)
		\begin{itemize}
			\item A simple checkbox to indicate whether the playback will start the designated audio track when the preview playback is started. 
		\end{itemize}
		\item Manage Preview Playback
		 \begin{itemize}
		     \item Start\textbackslash Pause : The traditional Play triangle and double-bars Pause button to start and pause the preview playback.
		     \item Adjust playback speed : A few playback speed presets (0.5x 0.75x, 1x, 1.25x, 1.5x), default is 1x speed.
		     \item Stop : Traditional Stop button with square icon to stop the preview playback.
		 \end{itemize}
	\end{itemize}
	
% 	\subsection{Notes}
% 	\begin{itemize}
% 		\item 
% 		\item 
% 		\item 
% 	\end{itemize}
\section{Additional Features}
	\subsection{Preview Slider} The Preview window will have a "preview area" that shows the timeline of the current show. The preview area will also have a slider which can be dragged back and forth along the timeline to control the preview playback.
\end{document}
